---
title: "Valency patterns in Mande: contact vs inheritance"
author: 
  - Maria Khachaturyan
  - Valentin Vydrin
  - Maria Konoshenko
  - George Moroz
date: "02/06/2024"
date-format: "D.MM.YYYY"
format: 
  beamer:
    theme: Singapore
    mainfont: Brill
    monofont: Iosevka
    df-print: kable
    pdf-engine: xelatex
    cite-method: natbib
    classoption: t
    header-includes: |
       \setbeamertemplate{footline}[page number]
urlcolor: teal
citecolor: teal
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
library(tidyverse)
# setwd("/home/agricolamz/work/materials/2024.02.06_Mande")
df <- readxl::read_xlsx("data/data.xlsx")
theme_set(theme_minimal()+theme(text = element_text(size = 14)))
```


# Introduction

# On Mande languages

# Data collection and coding

## Data source

Data were collected with the help of the [BivalTyp](https://bivaltyp.info/) [@saj20] questionnaire focusing on bivalent predicates and containing 130 stimulus sentences. The Russian variant of the questionnaire, which we then translated into French and used in our fieldwork.

. . .

- elicitation 
    - Kono (Southwestern)
    - Kpelle (Southwestern)
    - Mano (Southern)
- published data based on the questionnaire
    - Looma (Southwestern) (Mishchenko 2018)
    - Guro (Southern) [@kuznetsova18; @kuznetsova21]
    - Dan-Gweetaa (Southern) [@vydrin21]
    - Bamana (Manding) [@dumestre11; @bailleul11]

## Data

Resulting database does not have exactly 130 equivalents per language:

- some stimulus meanings do not have a straightforward equivalent
- some pairs of stimuli showed identical equivalents, so we excluded stimuli 112, 114, 122, 125, and 128
- we collected all equivalent per stimulus predicate

```{r}
df |> 
  count(language) |> 
  arrange(n) |> 
  rename(`N stimuli` = n)
```


# Results

# Conclussion

# References {.allowframebreaks}
